### 2024-07-12 analysis/analysis.qmd

```{r}
#| warning: false
#| eval: true
library(dmetar)
library(tidyverse)
library(meta)

R_studies <- read.csv("R_studies.csv")
R_summary <- read.csv("R_summary.csv")

@@

```{r}
outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")

@@

```{r}
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE,
       prediction = TRUE)

@@

>>>>

```{r}
#| warning: false
#| eval: true
library(dmetar)
library(tidyverse)
library(meta)
library(DescTools)
library(ggrepel)
#R_studies <- read.csv("R_studies.csv")
R_summary <- read.csv("R_summary.csv")

@@

```{r}
#| eval: false
outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")

@@

add `journal_type` and `stimulus_genre_mixed` as a grouping option

```{r}
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

@@

## Classification studies

C_studies <- read.csv("C_studies.csv")
C_studies <- C_studies[!is.na(C_studies$values),]

C_summary <- read.csv("C_summary.csv")

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = C_summary,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Classification: Summary")

#m.cor_backtransformed <- m.cor
#m.cor_backtransformed$TE <- FisherZInv(m.cor_backtransformed$TE)
print(funnel(m.cor, common = FALSE, studlab=TRUE,backtransf=TRUE))

```{r}
library(ggrepel)
tmpdata <- data.frame(SE = FisherZInv(m.cor$seTE), Zr = FisherZInv(m.cor$TE),studies=m.cor$studlab)

g <- ggplot(tmpdata,aes(y = SE, x = Zr,label=studies,color=citekey,fill=citekey)) +
  geom_point(show.legend = FALSE) +
  geom_label_repel(size=1.5,max.overlaps = 39,color="black",show.legend = FALSE)+
  ylab('Standard Error') + 
  xlab('r')+
  scale_y_reverse()+
#  scale_x_continuous(breaks=seq(0.0,1.0,0.25),limits=c(0,1.0))+
#  coord_flip()+
  theme_bw()
print(g)
```

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
#infan <- InfluenceAnalysis(m.cor)
#print(eggers.test(m.cor))

```{r}
#| eval: false
outliers <- c("")

```{r}
#| eval: false
tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
estimate = m.cor$TE.common
se = m.cor$seTE.common
se.seq=seq(0, max(m.cor$cor), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

add `journal_type` and `stimulus_genre_mixed` as a grouping option

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)
